Online Tuning of EASY-Backfilling using Queue Reordering Policies.

### 2018-03-09 paper/paper.tex
added Index term
paper modif

@@

>>>>

\IEEEtitleabstractindextext{D.4.7.f Parallel Systems, D.4.1.e Scheduling, 1.2.6 Learning}

@@

\begin{IEEEbiographynophoto}{Eric Gaussier}
Biography text here.
\end{IEEEbiographynophoto}

\begin{IEEEbiographynophoto}{J\'er\^ome Lelong}
Biography text here.
\end{IEEEbiographynophoto}

\begin{IEEEbiographynophoto}{Valentin Reis}
Valentin is a PhD candidate at Inria/University Grenoble Alpes, France.
He is broadly interested in machine learning and functionnal programming.
\end{IEEEbiographynophoto}

\begin{IEEEbiographynophoto}{Denis Trystram}
Biography text here.
\end{IEEEbiographynophoto}
